gavin_thesis_R

### 2025-02-15 notebooks/gavin_thesis_markdown.qmd
final

```{r}
#| label: fig-methodplot
#| fig-width: 8
#| fig-height: 5
#| fig-cap: "**Vein-specific susceptibility and oxygen saturation values by method.** (A, B) contains violin plots comparing subject chi (ppm) acquired from the cerebral central veins; (C, D) contains violin plots comparing subject SvO2 (%) acquired from the superior sagittal sinus. Raw data points from paramagnetic maps are shown as filled green circles and raw data points from QSM are shown as filled orange circles. Each line connects the raw data points of a single subject. (***) indicates P<0.05."
patch1
```

# Region analysis: Chi and CSvO2

@@

```{r}
#| label: fig-regionplot
#| fig-width: 8
#| fig-height: 5
#| fig-cap: "**Inter-venous comparisons of susceptibility and oxygen saturation**. Violin plots comparing (A, C) chi (ppm) and (B, D) SvO2 (%) between the CCV and the SSS. Panels (A) and (B) used data acquired from QSM, and its raw data points are shown as filled orange circles. Panels (C) and (D) used data acquired from paramagnetic maps, and its raw data points are shown as filled green circles. Each line connects the raw data points of a single subject. (***) indicates p<0.05; (n.s.) indicates no significant difference."
patch2
```

>>>>

```{r}
#| label: fig-methodplot
#| fig-width: 8
#| fig-height: 5
#| fig-cap: "**Vein-specific susceptibility and oxygen saturation values by method.** (A, B) contains violin plots comparing subject chi (ppm) acquired from the cerebral central veins; (C, D) contains violin plots comparing subject SvO2 (%) acquired from the superior sagittal sinus. Raw data points from paramagnetic maps are shown as filled green circles and raw data points from QSM are shown as filled orange circles. Each line connects the raw data points of a single subject. (***) indicates P<0.05."
patch1
```
```{r}
ggsave("Figure4.png", plot = patch1, dpi = 300, width = 8, height = 5, units = "in")
```
# Region analysis: Chi and CSvO2

@@

```{r}
#| label: fig-regionplot
#| fig-width: 8
#| fig-height: 5
#| fig-cap: "**Inter-venous comparisons of susceptibility and oxygen saturation**. Violin plots comparing (A, C) chi (ppm) and (B, D) SvO2 (%) between the CCV and the SSS. Panels (A) and (B) used data acquired from QSM, and its raw data points are shown as filled orange circles. Panels (C) and (D) used data acquired from paramagnetic maps, and its raw data points are shown as filled green circles. Each line connects the raw data points of a single subject. (***) indicates p<0.05; (n.s.) indicates no significant difference."
patch2
```
```{r}
ggsave("Figure5.png", plot = patch2, dpi = 300, width = 8, height = 5, units = "in")
```
